---
title: "Ex 3.9 Markdown"
author: "Ace Skyhawk (with help from Prof Carver)"
output:
  word_document: default
  html_notebook: default
---

# Introduction
This document illustrates the use of an R Notebook and R Markdown to create a reproducible product in the R language. The example is based on Exercise 3.9 in *MDSR*. You can create simple paragraphs to document your work, and intersperse code junks along the way. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.


## Exercise 3.9 (page 61)
"Using the data from the `nasaweather` package, create a scatterplot between wind and pressure, with color being used to distinguish the type of storm"

We'll use ggplot2 to create the scatterplot using the data stored in `nasaweather`. Unfortunately, our server does not yet have the `nasaweather` package installed, so we first need to install it, and then invoke it with a `library` command, and then look at the structure of the dataframe.  

```{r}
# install.packages("nasaweather")  having once installed no need to install again.
library(nasaweather)
library(ggplot2)
str(storms)
```

From the `str` output, we see the names of the variables involved in the ggplot command, as follows:

```{r}
g <- ggplot(data=storms, aes(y=wind, x=pressure))
g <- g + geom_point(size=1)
g <- g + aes(color = type)
g <- g + ggtitle("Wind and Pressure by Storm Type")
g

```
  
## Conclusion  

It appears that there is generally a negative relationship between temperature and pressure, and that different storm types have characteristic patterns of wind and pressure.



